---
title: "Earth Agency - DependentVariables by Age"
author: "Consulting Group 3"
date: "2/23/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("knitr")
library("kableExtra")
library("gridExtra") 
library("ggplot2")
library("plyr")
library("dplyr")
```

```{r, include=FALSE}
#Change working directory to your own
setwd("~/MSSP/Consulting/EarthAgencyProject")
adult <- read.csv("EarthAgency_Adults_R.csv", header = TRUE)
children <- read.csv("EarthAgency_Children_R.csv", header = TRUE)

adult1 <- adult %>%
  dplyr::select(
    Condition,
    Agency_Language,
    SRFactsTotal,
    SRTotal,
    invitalscore,
    inpsychscore,
    inagencyscore,
    Gender,
    MeanSever,
    BioJtscore,
    AntJtscore,
    BioJFtotal,
    Sciclass,
    FirstLang
  ) %>%
  mutate(Condition = factor(Condition))

adult1 <- na.omit(adult1)
adult1 <- adult1 %>%
  mutate(
    SRFactsTotal = as.integer(SRFactsTotal),
    inagencyscore = as.integer(inagencyscore),
    invitalscore = as.integer(invitalscore),
    inpsychscore = as.integer(inpsychscore),
    Gender = as.factor(Gender),
    Agency_Language = as.factor(Agency_Language),
    Sciclass = as.factor(Sciclass),
    FirstLang = as.factor(FirstLang)
  )

children1 <- children %>%
  dplyr::select(
    Condition,
    Agency_Language,
    SRFactsTotal,
    SRTotal,
    invitalscore,
    inpsychscore,
    inagencyscore,
    Location,
    Gender,
    Order,
    MeanSever,
    BioJtscore,
    AntJtscore,
    BioJFtotal
  ) %>%
  mutate(Condition = factor(Condition))

children1$OrderS <- substring(children1$Order, 1, 2)
children1 <- na.omit(children1)

children1 <- children1 %>%
  mutate(
    SRFactsTotal = as.integer(SRFactsTotal),
    inagencyscore = as.integer(inagencyscore),
    invitalscore = as.integer(invitalscore),
    inpsychscore = as.integer(inpsychscore),
    Gender = as.factor(Gender),
    Location = as.factor(Location),
    Agency_Language = as.factor(Agency_Language),
    OrderS = as.factor(OrderS)
  )
#To take care of the one errant entry
children1$MeanSever[children1$MeanSever==2.67] <- 2.5

##-------------
## COMBINING children and adult into one data.frame
#Create children's data frame
df_c <- children %>% 
  select(
    MeanSever, BioJtscore, AntJtscore, BioJFtotal, Condition
    )
Age <- rep("child", nrow(df_c))
df_c <- df_c %>% mutate(Age)


#To take care of the one errant entry
df_c$MeanSever[df_c$MeanSever==2.67] <- 2.5

#Create adult's data frame
df_a <- adult %>% 
  select(
    MeanSever, BioJtscore, AntJtscore, BioJFtotal, Condition
  )
Age <- rep("adult", nrow(df_a))
df_a <- df_a %>% mutate(Age)

df <- bind_rows(df_c, df_a)

###NOTE: Children$MeanSever[87] = 2.67 (BUT, mean severity scores are divided by 4 so .67 is not possible…).  We've coerced it to be 2.5, but  the validity of this score should be checked.

```

## 1.1 Original Mean Severity scores subsetted by Age and Condition

```{r echo=FALSE, warning=FALSE, fig.height=4.5}

adult1$Condition <- revalue(adult1$Condition, c("1"="Object", "2"="Nature", "3"="Person"))
children1$Condition <- revalue(children1$Condition, c("1"="Object", "2"="Nature", "3"="Person"))

Adlts <- ggplot(data=adult1, aes(MeanSever, y=..count../sum(..count..), fill=Condition)) +
  geom_bar(color="white", width=.125) +
  labs(title="Adults", x="Mean Severity Score (original)", y="Proportion") +
  coord_cartesian(ylim=c(0, .2), xlim=c(0,3)) +
  theme(axis.line.y=element_line(color="black", size=.5),
        panel.background = element_blank(), 
        panel.grid.major.x = element_line(color="grey", size=0.25),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_line(color="grey", size=0.25),
        panel.grid.minor.y = element_blank(),
        legend.position = c(.90, .85),
        legend.title = element_text(size=8),
        legend.text = element_text(size=7)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))

chldrn <- ggplot(data=children1, aes(MeanSever, y=..count../sum(..count..), fill=Condition)) +
  geom_bar(color="white", width=.125) +
  labs(title="Children", x="Mean Severity Score (original)", y="")  +
  coord_cartesian(ylim=c(0, .2), xlim=c(0,3)) +
  guides(fill="none") +
  theme(axis.line.y=element_line(color="grey", size=.25),
        panel.background = element_blank(), 
        panel.grid.major.x = element_line(color="grey", size=0.25),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_line(color="grey", size=0.25),
        panel.grid.minor.y = element_blank()) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))

grid.arrange(Adlts, chldrn, ncol=2)
```
\newpage

## 1.2 Original Mean Severity scores and grouped Mean Severity scores  
```{r echo=FALSE, message=FALSE, fig.height=3}

#Calculate % in each of the 13 MeanSeverity outcomes for children
df_c_MS <- df_c %>% 
  group_by(MeanSever) %>% 
  summarise(n=n(), Age="child") %>% 
  mutate(prop=n/sum(n))

#Calculate % in each of the 13 MeanSeverity outcomes for Adults
df_a_MS <- df_a %>% 
  group_by(MeanSever) %>% 
  summarise(n=n(), Age="adult") %>% 
  mutate(prop=n/sum(n))

df_MS <- bind_rows(df_c_MS, df_a_MS)

par(mfrow=c(2,1))

ggplot(df_MS, aes(x=MeanSever, y=prop, fill=Age)) +
  geom_col(color="white", position = position_dodge2(width = 0.001, preserve = "single")) +
  labs(x="Mean Severity Score (original)", y="Proportion") +
  coord_cartesian(ylim=c(0, .2), xlim=c(0,3)) +
  theme(axis.line.y=element_line(color="black", size=.5),
        panel.background = element_blank(), 
        panel.grid.major.x = element_line(color="grey", size=0.25),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_line(color="grey", size=0.25),
        panel.grid.minor.y = element_blank(),
        legend.position = c(.15, .84)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))

table_MS <- data.frame(
  Severity_Score=seq(0,3,length.out=13),
  Adults = as.numeric(df_MS$n[df_MS$Age=="adult"]),
  children = as.numeric(rep(0,13))
  )
table_MS$children[3:13] <- df_MS$n[df_MS$Age=="child"]
table_MS <- mutate(table_MS, TOTAL=Adults+children)
table_MS$Adults <- format(table_MS$Adults, digits=2, nsmall=0)
table_MS$children <- format(table_MS$children, digits=2, nsmall=0)
table_MS$TOTAL <- format(table_MS$TOTAL, digits=2, nsmall=0)

kable(t(table_MS))

```
  
0 = "ok", 1 = "wrong", 2 = "very wrong", 3 = "extremely wrong"  
\newline
\newline
  
```{r echo=FALSE, message=FALSE, fig.height=3}

#To group the scores into {1, 2, 3}
df_c$MeanSever[df_c$MeanSever<1.1] <- 1
df_c$MeanSever[df_c$MeanSever>1 & df_c$MeanSever<2.1] <- 2
df_c$MeanSever[df_c$MeanSever>2 &df_c$MeanSever<3.1] <- 3

#Calculate % in each of the 3 grouped MeanSeverity outcomes for children
df_c_MS <- df_c %>% 
  group_by(MeanSever) %>% 
  summarise(n=n(), Age="child") %>% 
  mutate(prop=n/sum(n))

#To group the scores into {1, 2, 3}
df_a$MeanSever[df_a$MeanSever<1.1] <- 1
df_a$MeanSever[df_a$MeanSever>1 & df_a$MeanSever<2.1] <- 2
df_a$MeanSever[df_a$MeanSever>2 & df_a$MeanSever<3.1] <- 3

#Calculate % in each of the 3 grouped MeanSeverity outcomes for children
df_a_MS <- df_a %>% 
  group_by(MeanSever) %>% 
  summarise(n=n(), Age="adult") %>% 
  mutate(prop=n/sum(n))

df_MS <- bind_rows(df_c_MS, df_a_MS)

par(mfrow=c(2,1))
ggplot(df_MS, aes(x=MeanSever, y=prop, fill=Age)) +
  geom_col(color="white", position = position_dodge2(width = 0.001, preserve = "single")) +
  labs(x="Mean Severity Score (grouped)", y="Proportion") +
  coord_cartesian(ylim=c(0, .6), xlim=c(0,3.5)) +
  theme(axis.line.y=element_line(color="black", size=.5),
        panel.background = element_blank(), 
        panel.grid.major.x = element_line(color="grey", size=0.25),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_line(color="grey", size=0.25),
        panel.grid.minor.y = element_blank(),
        legend.position = c(.15, .84)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))

table_MS <- data.frame(
  Severity_Score=c(1:3),
  Adults = as.numeric(df_MS$n[df_MS$Age=="adult"]),
  children = as.numeric(df_MS$n[df_MS$Age=="child"])
  )
table_MS <- mutate(table_MS, TOTAL=Adults+children)
table_MS$Adults <- format(table_MS$Adults, digits=2, nsmall=0)
table_MS$children <- format(table_MS$children, digits=2, nsmall=0)
table_MS$TOTAL <- format(table_MS$TOTAL, digits=2, nsmall=0)

kable(t(table_MS))
```
  
1 = "ok or wrong" ($original \le 1$), 2 = "very wrong" ($original \le 2$), 3 = "extremely wrong" ($original \le 3$)  
\newpage

## 2.1 Justifications citing Biocentric reasons
```{r echo=FALSE, warning=FALSE, fig.height=2.75}

#Remove the one NA in BioJtscore (and AntJtscore)
df_c <- df_c[!is.na(df_c$BioJtscore), ]

#Calculate % in each of the 5 BioJtscore outcomes for children

df_c_BC <- df_c %>% 
  group_by(BioJtscore) %>% 
  summarise(n=n(), Age="child") %>% 
  mutate(prop=n/sum(n))

#Calculate % in each of the 5 BioJtscore outcomes for Adults
df_a_BC <- df_a %>% 
  group_by(BioJtscore) %>% 
  summarise(n=n(), Age="adult") %>% 
  mutate(prop=n/sum(n))

df_BC <- bind_rows(df_c_BC, df_a_BC)

par(mfrow=c(2,1))
ggplot(df_BC, aes(x=BioJtscore, y=prop, fill=Age)) +
  geom_col(color="white", position = position_dodge2(width = 0.001, preserve = "single")) +
  labs(x="Justifications citing biocentric reason", y="Proportion") +
  coord_cartesian(ylim=c(0, .45), xlim=c(-0.5,4.5)) +
  theme(axis.line.y=element_line(color="black", size=.5),
        panel.background = element_blank(), 
        panel.grid.major.x = element_line(color="grey", size=0.25),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_line(color="grey", size=0.25),
        panel.grid.minor.y = element_blank(),
        legend.position = c(.1, .84)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))

table_BC <- data.frame(
  Biocentric_Score=0:4,
  Adults = as.numeric(df_BC$n[df_BC$Age=="adult"]),
  children = as.numeric(df_BC$n[df_BC$Age=="child"])
  )
table_BC <- mutate(table_BC, TOTAL=Adults+children)
table_BC$Adults <- format(table_BC$Adults, digits=2, nsmall=0)
table_BC$children <- format(table_BC$children, digits=2, nsmall=0)
table_BC$TOTAL <- format(table_BC$TOTAL, digits=2, nsmall=0)

kable(t(table_BC))

### NOTES: children$BioJtscore[41]=NA and children$AntJtscore[41]=NA We've removed this record.  Is there a correct score for this record?
```

## 3.1 Justifications citing Anthropocentric reasons
```{r echo=FALSE, warning=FALSE, fig.height=2.75}

#Calculate % in each of the 5 AntJtscore outcomes for children
df_c_AC <- df_c %>% 
  group_by(AntJtscore) %>% 
  summarise(n=n(), Age="child") %>% 
  mutate(prop=n/sum(n))

#Calculate % in each of the 5 AntJtscore outcomes for Adults
df_a_AC <- df_a %>% 
  group_by(AntJtscore) %>% 
  summarise(n=n(), Age="adult") %>% 
  mutate(prop=n/sum(n))

df_AC <- bind_rows(df_c_AC, df_a_AC)

par(mfrow=c(2,1))
ggplot(df_AC, aes(x=AntJtscore, y=prop, fill=Age)) +
  geom_col(color="white", position = position_dodge2(width = 0.001, preserve = "single")) +
  labs(x="Justifications citing antrhopocentric reason", y="Proportion") +
  coord_cartesian(ylim=c(0, .45), xlim=c(-0.5,4.5)) +
  theme(axis.line.y=element_line(color="black", size=.5),
        panel.background = element_blank(), 
        panel.grid.major.x = element_line(color="grey", size=0.25),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_line(color="grey", size=0.25),
        panel.grid.minor.y = element_blank(),
        legend.position = c(.1, .84)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))

table_AC <- data.frame(
  Anthrocentric_Score=0:4,
  Adults = as.numeric(df_AC$n[df_AC$Age=="adult"]),
  children = as.numeric(df_AC$n[df_AC$Age=="child"])
  )
table_AC <- mutate(table_AC, TOTAL=Adults+children)
table_AC$Adults <- format(table_AC$Adults, digits=2, nsmall=0)
table_AC$children <- format(table_AC$children, digits=2, nsmall=0)
table_AC$TOTAL <- format(table_AC$TOTAL, digits=2, nsmall=0)

kable(t(table_AC))
```

## 4.1 Given the choice (Biocentric or Anthopocentric), number of Biocentric justifications chosen
```{r echo=FALSE, warning=FALSE, fig.height=2.75}

#Calculate % in each of the 4 BioFtotal outcomes for children
df_c_BorA <- df_c %>% 
  group_by(BioJFtotal) %>% 
  summarise(n=n(), Age="child") %>% 
  mutate(prop=n/sum(n))

#Calculate % in each of the 5 BioFtotal outcomes for Adults
df_a_BorA <- df_a %>% 
  group_by(BioJFtotal) %>% 
  summarise(n=n(), Age="adult") %>% 
  mutate(prop=n/sum(n))

#Row to include the fact that there were no BioJtotal=0 for the adults
df_a_empty <- data.frame(
  BioJFtotal = 0,
  n = 0,
  Age = "adult",
  prop = 0.0
)

df_BorA <- bind_rows(df_c_BorA, df_a_empty, df_a_BorA)

par(mfrow=c(2,1))
ggplot(df_BorA, aes(x=BioJFtotal, y=prop, fill=Age)) +
  geom_col(color="white", position = position_dodge2(width = 0.001, preserve = "single")) +
  labs(x="Number of Biocentric chosen", y="Proportion") +
  coord_cartesian(ylim=c(0, .60), xlim=c(-0.5,4.5)) +
  theme(axis.line.y=element_line(color="black", size=.5),
        panel.background = element_blank(), 
        panel.grid.major.x = element_line(color="grey", size=0.25),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_line(color="grey", size=0.25),
        panel.grid.minor.y = element_blank(),
        legend.position = c(.1, .84)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))

table_BorA <- data.frame(
  Numb_Bio_Chosen=0:4,
  Adults = as.numeric(df_BorA$n[df_BorA$Age=="adult"]),
  children = as.numeric(df_BorA$n[df_BorA$Age=="child"])
  )
table_BorA <- mutate(table_BorA, TOTAL=Adults+children)
table_BorA$Adults <- format(table_BorA$Adults, digits=2, nsmall=0)
table_BorA$children <- format(table_BorA$children, digits=2, nsmall=0)
table_BorA$TOTAL <- format(table_BorA$TOTAL, digits=2, nsmall=0)

kable(t(table_BorA))
```
\newpage 
## 5.1 Correlation between Condition and Phase 3 questionnaire?
For each of the four comparisons shown, the Fisher test p-value is given.  We did a Fisher test because the conditions for a Pearson's Chi-squared test (all expected values $\ge$ 5) were not met.  
\newline
```{r echo=FALSE, warning=FALSE, fig.height=3.5}
ft.1 <- round(fisher.test(table(adult1$Condition, adult1$invitalscore))$p.value, 3)
gg.1 <- ggplot(adult1, aes(x=Condition, fill = factor(invitalscore))) +
  geom_bar() +
  scale_fill_hue() +
  theme_minimal(base_size=10) +
  scale_x_discrete(labels = c('Object','Nature','Human')) +
  guides(fill=guide_legend(title="")) +
  labs(title = "Adults (invitalscore)", 
       subtitle = paste("p-value = ", ft.1))

ft.2 <- round(fisher.test(table(adult1$Condition, adult1$inpsychscore))$p.value, 3)
gg.2 <- ggplot(adult1) +
  aes(x=Condition, fill = factor(inpsychscore)) +
  geom_bar() +
  scale_fill_hue() +
  theme_minimal(base_size=10) +
  scale_x_discrete(labels = c('Object','Nature','Human')) +
  guides(fill=guide_legend(title="")) +
  labs(title = "Adults (inpsychscore)", 
       subtitle = paste("p-value = ", ft.2))

ft.3 <- round(fisher.test(table(children1$Condition, children1$invitalscore))$p.value, 3)
gg.3 <- ggplot(children1) +
  aes(x=Condition, fill = factor(invitalscore)) +
  geom_bar() +
  scale_fill_hue() +
  theme_minimal(base_size=10) +
  scale_x_discrete(labels = c('Object','Nature','Human')) +
  guides(fill=guide_legend(title="")) +
  labs(title = "Children (invitalscore)", 
       subtitle = paste("p-value = ", ft.3))

ft.4 <- round(fisher.test(table(children1$Condition, children1$inpsychscore))$p.value, 3)
gg.4 <- ggplot(children1) +
  aes(x=Condition, fill = factor(inpsychscore)) +
  geom_bar() +
  scale_fill_hue() +
  theme_minimal(base_size=10) +
  scale_x_discrete(labels = c('Object','Nature','Human')) +
  guides(fill=guide_legend(title="")) +
  labs(title = "Children (inpsychscore)", 
       subtitle = paste("p-value = ", ft.4))

grid.arrange(gg.1, gg.2, ncol=2)
```
\newline
\newline
\newline
\newline
```{r echo=FALSE, warning=FALSE, fig.height=3.5}
    grid.arrange(gg.3, gg.4, ncol=2)
```
    