---
title: "Earth Agency Project Update"
author: "Consulting Group C3"
date: "2/12/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
pacman::p_load("knitr","tidyverse","glmnet","car","tidyverse","ggplot2","arm","rstanarm", "magrittr", "brant")
```

```{r, include=FALSE}
#Change working directory, can change to your own
setwd("~/MSSP/Consulting/Earth agency")
adult <- read.csv("EarthAgency_Adults_R.csv", header = TRUE)
children <- read.csv("EarthAgency_Children_R.csv", header = TRUE)

adult1 <- adult %>%
  dplyr::select(
    Condition,
    Agency_Language,
    SRFactsTotal,
    SRTotal,
    invitalscore,
    inpsychscore,
    inagencyscore,
    Gender,
    MeanSever,
    BioJtscore,
    AntJtscore,
    BioJFtotal,
    Sciclass,
    FirstLang
  ) %>%
  mutate(Condition = factor(Condition))

adult1 <- na.omit(adult1)
adult1 <- adult1 %>%
  mutate(
    SRFactsTotal = as.integer(SRFactsTotal),
    inagencyscore = as.integer(inagencyscore),
    invitalscore = as.integer(invitalscore),
    inpsychscore = as.integer(inpsychscore),
    Gender = as.factor(Gender),
    Agency_Language = as.factor(Agency_Language),
    Sciclass = as.factor(Sciclass),
    FirstLang = as.factor(FirstLang)
  )

children1 <- children %>%
  dplyr::select(
    Condition,
    Agency_Language,
    SRFactsTotal,
    SRTotal,
    invitalscore,
    inpsychscore,
    inagencyscore,
    Location,
    Gender,
    Order,
    MeanSever,
    BioJtscore,
    AntJtscore,
    BioJFtotal
  ) %>%
  mutate(Condition = factor(Condition))

children1$OrderS <- substring(children1$Order, 1, 2)
children1 <- na.omit(children1)

children1 <- children1 %>%
  mutate(
    SRFactsTotal = as.integer(SRFactsTotal),
    inagencyscore = as.integer(inagencyscore),
    invitalscore = as.integer(invitalscore),
    inpsychscore = as.integer(inpsychscore),
    Gender = as.factor(Gender),
    Location = as.factor(Location),
    Agency_Language = as.factor(Agency_Language),
    OrderS = as.factor(OrderS)
  )
```
# 1 Summary
There are four dependent variables of interest (MeanS, Bio, comAntJscore, comBioJFtotal).  Previous analysis convinced us to combine the levels of these variables in the following manner: 

For Children:  

Variable | Original levels | We combined | New levels
----------- | ----------- | ----------- | -----------
MeanSeverity | 0, 1, 2, 3  | 1 & 2 | 0, 1, 3, 4  
Bio | ?  | ? | ?  
comAntJscore | ?  | ? | ?  
comBioJFtotal | ?  | ? | ?  

For Adults: 

Variable | Original levels | We combined | New levels
----------- | ----------- | ----------- | -----------
MeanSeverity | 0, 1, 2, 3  | 0 & 1 | 0, 2, 3  
Bio | ?  | ? | ?  
comAntJscore | ?  | ? | ?  
comBioJFtotal | ?  | ? | ?  

For each of these eight dependent variables (4 for children, 4 for adults) we have included the following  six predictor variables in an ordinal regression model:  
  Condition, Agency_Language, SRFactsTotal, SRTotal, Gender, inagencyscore.  
For children we have added: Location & OrderS
For adults we have added: FirstLang

Previous analysis has convinced us to use an ordinal regression model.

The models and their summaries are organized below: 

# 2.1.1 Children: Mean Severity Score
```{r echo=FALSE, message=FALSE, warning=FALSE}


#Round and combine levels for Mean Severity (0=ok, 1=wrong, 2=very wrong, 3=extremely wrong):
#NOTE: the round() function rounds 0.5 down to 0 and 1.5 up to 2
# 0 => average score ≤ 0.5
# 1 => average score > 0.5 & ≤ 2.5
# 3 => average score > 2.5

#bcm.NOTE1: The round() function rounds 0.5 down to 0 and 1.5 up to 2.
#bcm.NOTE2: when I combine MeanS levels 1 & 2, then polr() doesn't run with three levels (line 81), so to get polr() to run the previous group added a fourth group (level 4) that has 0 values in it.  With the dummy forth level, and levels (0, 1, 3, 4), polr() runs (line 80).  When I combine levels 0 & 1, I can run polr() with three levels (1, 2, 3) BUT the p-value for the new 1|2 cut is 0.53.  The previous group made the decision to combine 1 & 2 because with the original four levels (0, 1, 2, 3) the cut-level for 1|2 was 0.46.
children1$MeanS <- round(children1$MeanSever, digits = 0)
children1$MeanS[which(children1$MeanS == 2)] <- 1
children1$MeanS <- factor(children1$MeanS, levels = c("0", "1", "3", "4"), ordered = TRUE)
#children1$MeanS <- factor(children1$MeanS, levels = c("0","2","3"),ordered = TRUE)

#Build ordinal logistic regression model
fit1_1 <- polr(
    MeanS ~ Condition + Agency_Language + SRFactsTotal + SRTotal + Gender + Location + inagencyscore + OrderS,
    data = children1
  )
summary(fit1_1)

#Get p-value (this is NOT done correctly - or is it? - need to fix?)
ctable <- coef(summary(fit1_1))
#p2 <- 2*pt(-abs(ctable[, "t value"]),df=length(children1$MeanS)-9)
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = p)
#ctable2 <- cbind(ctable, "p value" = p2)

ctable1

#Chi-square test
drop1(fit1_1, test = "Chi")

#Compute confusion table and misclassification error
fitted <- predict(fit1_1)
n <- table(children1$MeanS, fitted)
percantage <-
  c(n[1, 1] / sum(n[1, ]), n[2, 2] / sum(n[2, ]), n[3, 3] / sum(n[3, ]))
rbind(n, percantage)
ME <- mean(as.character(children1$MeanS) != as.character(fitted))
cat("Misclassification error is:", ME, "\n")

#Plotting the binned residual plot
obsmat <- model.matrix( ~ MeanS - 1, data = children1)
resdimat <- obsmat - fitted(fit1_1)
par(mfrow = c(2, 2))

binnedplot(fitted(fit1_1)[, 1], resdimat[, 1])
binnedplot(fitted(fit1_1)[, 2], resdimat[, 2])
binnedplot(fitted(fit1_1)[, 3], resdimat[, 3])

brant(fit1_1)
```

# 2.1.2 Adults: Mean Severity Score
```{r echo=FALSE, message=FALSE, warning=FALSE}
#Round and combine levels for Mean Severity (0=ok, 1=wrong, 2=very wrong, 3=extremely wrong),
#NOTE: the round() function rounds 0.5 down to 0 and 1.5 up to 2
# 0 => average score ≤ 1.25
# 2 => average score > 1.5 & ≤ 2.5
# 3 => average score > 2.5

# adult1$MeanSeverity<-round(adult1$MeanSever)
# adult1$MeanSeverity <- factor(adult1$MeanSeverity,levels = c("0","1","2","3"),ordered = TRUE)
#
# fit1_2 <- polr(MeanSeverity ~ Condition + Agency_Language + SRFactsTotal + SRTotal + Gender + inagencyscore, data = adult1)
# summary(fit1_2) #AIC: 303.7906
#
# adult1$MeanS<-adult1$MeanSever
adult1$MeanS <- round(adult1$MeanSever, digits = 0)
adult1$MeanS[which(adult1$MeanS == 1)] <- 0
adult1$MeanS <- factor(adult1$MeanS, levels = c("0", "2", "3"), ordered = TRUE)

fit1_2 <- polr(
  MeanS ~ Condition + Agency_Language + SRFactsTotal + SRTotal + Gender + inagencyscore + FirstLang, 
  data = adult1
)
summary(fit1_2)

#Get p-value
ctable <- coef(summary(fit1_2))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable <- cbind(ctable, "p value" = p)
ctable

#Chi-square test
drop1(fit1_2, test = "Chi")

#Compute confusion table and misclassification error
fitted <- predict(fit1_2)
n <- table(adult1$MeanS, fitted)
percantage <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]))
rbind(n, round(percantage, digits = 2))
ME <-
  mean(as.character(adult1$MeanS) != as.character(fitted))
cat("Misclassification error is:", ME, "\n")

#Plotting the binned residual plot,
obsmat <- model.matrix( ~ MeanS - 1, data = adult1)
resdimat <- obsmat - fitted(fit1_2)
par(mfrow = c(2, 2))

binnedplot(fitted(fit1_2)[, 1], resdimat[, 1])
binnedplot(fitted(fit1_2)[, 2], resdimat[, 2])
binnedplot(fitted(fit1_2)[, 3], resdimat[, 3])

brant(fit1_2)
```
