---
title: "Earth Agency Project Update"
author: "Consulting Group C3"
date: "2/12/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
pacman::p_load("knitr","tidyverse","glmnet","car","tidyverse","ggplot2","arm","rstanarm", "magrittr", "brant")
```

```{r, include=FALSE}
#Change work directory, can change to your own
setwd("~/MSSP/Consulting/Earth agency")
adult <- read.csv("EarthAgency_Adults_R.csv",header = TRUE)
children <- read.csv("EarthAgency_Children_R.csv",header = TRUE)

adult1 <- adult %>%
            dplyr::select(Condition,Agency_Language,SRFactsTotal,SRTotal,invitalscore,
                   inpsychscore,inagencyscore,Gender,
                   MeanSever,BioJtscore,AntJtscore,BioJFtotal,Sciclass,FirstLang)%>%
                   mutate(Condition = factor(Condition))
adult1 <- na.omit(adult1)
adult1 <- adult1 %>%
                 mutate(SRFactsTotal=as.integer(SRFactsTotal),inagencyscore=as.integer(inagencyscore),invitalscore=as.integer(invitalscore),inpsychscore=as.integer(inpsychscore),Gender=as.factor(Gender),Agency_Language=as.factor(Agency_Language),Sciclass=as.factor(Sciclass),FirstLang=as.factor(FirstLang))



children1 <- children %>%
            dplyr::select(Condition,Agency_Language,SRFactsTotal,SRTotal,invitalscore,
                   inpsychscore,inagencyscore,Location,Gender,Order,
                   MeanSever,BioJtscore,AntJtscore,BioJFtotal) %>%
                   mutate(Condition = factor(Condition))
children1$OrderS <- substring(children1$Order, 1, 2)
children1 <- na.omit(children1)
children1 <- children1 %>%
                 mutate(SRFactsTotal=as.integer(SRFactsTotal),inagencyscore=as.integer(inagencyscore),invitalscore=as.integer(invitalscore),inpsychscore=as.integer(inpsychscore),Gender=as.factor(Gender),Location=as.factor(Location),Agency_Language=as.factor(Agency_Language),OrderS=as.factor(OrderS))
```
# 1 Summary
There are four dependent variables of interest (MeanS, Bio, comAntJscore, comBioJFtotal).  Previous analysis convinced us to combine the levels of these variables in the following manner: 

For Children:  

Variable | Original levels | We combined | New levels
----------- | ----------- | ----------- | -----------
MeanSeverity | 0, 1, 2, 3  | 1 & 2 | 0, 1, 3  
Bio | 0, 1, 2, 3  | 0 & 1 | 0, 1, 2  
comAntJscore | 0, 1, 2, 3  | 0 & 1 | 0, 1, 2  
comBioJFtotal | 0, 1, 2, 3  | 0 & 1 | 0, 1, 2  

For Adults: 

Variable | Original levels | We combined | New levels
----------- | ----------- | ----------- | -----------
MeanS | 0, 1, 2, 3  | 0 & 1 | 0, 1, 2  
Bio | 0, 1, 2, 3  | 0 & 1 | 0, 1, 2  
comAntJscore | 0, 1, 2, 3  | 0 & 1 | 0, 1, 2  
comBioJFtotal | 0, 1, 2, 3  | 0 & 1 | 0, 1, 2  

For each of these eight dependent variables (4 for children, 4 for adults) we have included the following  six predictor variables in an ordinal regression model: Condition, Agency_Language, SRFactsTotal, SRTotal, Gender, inagencyscore.  
For children we have added: Location & OrderS
For adults we have added: FirstLang

Previous analysis has convinced to use an ordinal regression model.

The models and their summaries are organized below: 

# 2.1.1 Children: Mean Severity Score
```{r echo=FALSE, message=FALSE, warning=FALSE}

#Round and combine levels for Mean Severity (0=ok, 1=wrong, 2=very wrong, 3=extremely wrong),
# 0 => average score ≤ 0.5
# 1 => average score > 0.5 & ≤ 2.5
# 3 => average score > 2.5

children1$MeanS<-children1$MeanSever
children1$MeanS<-round(children1$MeanS,digits=0)
children1$MeanS[which(children1$MeanS==2)]<-1
#children1$MeanS <- factor(children1$MeanS, levels = c("0","1","3", "4"),ordered = TRUE)
children1$MeanS <- factor(children1$MeanS, levels = c("0","1","3"),ordered = TRUE)

#Build ordinal logistic regression model                               
fit1_1 <- polr(MeanS ~ Condition + Agency_Language + SRFactsTotal + SRTotal + Gender + Location + inagencyscore + OrderS, data = children1)
summary(fit1_1)

#Get p-value (this is NOT done correctly - need to fix)
ctable <- coef(summary(fit1_1))
#p2 <- 2*pt(-abs(ctable[, "t value"]),df=length(children1$MeanS)-9)
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = p)
#ctable2 <- cbind(ctable, "p value" = p2)

ctable1

#Chi-square test
drop1(fit1_1,test="Chi")

#Compute confusion table and misclassification error
fitted <- predict(fit1_1)
n <- table(children1$MeanS,fitted)
percantage <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]))
rbind(n,percantage)
ME <- mean(as.character(children1$MeanS) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")

#Plotting the binned residual plot
obsmat <-model.matrix(~MeanS-1,data=children1)
resdimat<-obsmat-fitted(fit1_1)
par(mfrow=c(2,2))

binnedplot(fitted(fit1_1)[,1],resdimat[,1])
binnedplot(fitted(fit1_1)[,2],resdimat[,2])
binnedplot(fitted(fit1_1)[,3],resdimat[,3])

brant(fit1_1)
```
