---
title: "March 1 Report"
author: "Consulting Group 3"
date: "2/24/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(plyr)
```
## Code to create AC_df, the combined data.frame with all variables that we are investigating
```{r echo=FALSE}
#Change working directory to your own
setwd("~/MSSP/Consulting/EarthAgencyProject")
adult <- read.csv("EarthAgency_Adults_R.csv", header = TRUE)
children <- read.csv("EarthAgency_Children_R.csv", header = TRUE)

adult_df <- adult %>%
  dplyr::select(
    Condition,
    Agency_Language,
    SRFactsTotal,
    invitalscore,
    inpsychscore,
    MeanSever,
    BioJtscore,
    AntJtscore,
    BioJFtotal,
    FirstLang
  ) %>%
  mutate(
    Condition = as.factor(Condition),
    SRFactsTotal = as.integer(SRFactsTotal),
    invitalscore = as.integer(invitalscore),
    inpsychscore = as.integer(inpsychscore),
    Agency_Language = as.factor(Agency_Language),
    FirstLang = as.factor(FirstLang)
  )

#to add an age variable
Age <- rep("adult", nrow(adult_df))
adult_df <- adult_df %>% 
  mutate(Age)

#compress scores to match invitalscore and inpsychscore for children
adult_df$invitalscore[which(adult_df$invitalscore==0 | adult_df$invitalscore==1)]<-0
adult_df$invitalscore[which(adult_df$invitalscore==2) ]<-1
adult_df$invitalscore[which(adult_df$invitalscore==3) ]<-2
adult_df$invitalscore[which(adult_df$invitalscore==4 | adult_df$invitalscore==5)]<-3

adult_df$inpsychscore[which(adult_df$inpsychscore==2 | adult_df$inpsychscore==3)]<-2
adult_df$inpsychscore[which(adult_df$inpsychscore==4)]<-3
adult_df$inpsychscore[which(adult_df$inpsychscore==5)]<-4

child_df <- children %>%
  dplyr::select(
    Condition,
    Agency_Language,
    SRFactsTotal,
    invitalscore,
    inpsychscore,
    MeanSever,
    BioJtscore,
    AntJtscore,
    BioJFtotal
  ) %>%
  mutate(
    Condition = as.factor(Condition),
    SRFactsTotal = as.integer(SRFactsTotal),
    invitalscore = as.integer(invitalscore),
    inpsychscore = as.integer(inpsychscore),
    Agency_Language = as.factor(Agency_Language)
  )
Age <- rep("child", nrow(child_df))
#We're not sure we have the coding for FirstLang correct (1 = speaking their first language??)
FirstLang <- rep(1, nrow(child_df))
child_df <- child_df %>% 
  mutate(
    FirstLang = as.factor(FirstLang),
    Age
    )

#To take care of the one errant entry, children[87] (mean severity scores are divided by 4 so .67 is not possible…)
child_df$MeanSever[child_df$MeanSever==2.67] <- 2.5

#To remove children[41] which has no BIoJtscore or AntJtscore
#To remove children[45] which has no Agency_Language or SRFactsTotal
child_df <- na.omit(child_df)

## COMBINING children and adult into one data.frame
AC_df <- bind_rows(adult_df, child_df)

#Giving factor levels cleaner language
AC_df$Condition <- revalue(AC_df$Condition, c("1"="Obj", "2"="Nat", "3"="Per"))
AC_df$Agency_Language <- revalue(AC_df$Agency_Language, c("0"="Obj", "2"="Nat", "3"="Per"))

```
## Tasks
1) Verify the data decisions (with Lizette?) that are noted in the code chunk above.  
2) Fit the polr() model for each of the four dependent variables (MeanSever, BioJtscore, AntJtscore, BioJFtotal), using the independent variables (Condition, Agency_Language, SRFactsTotal, invitalscore, inpsychscore, FirstLang, Age)
3) Fit a linear regression model using same variables, and compare to the polr() model.  If it's comprable, then the interprebility of the linear model would argue for using it.
4) Check for multicollinearity in the models using the variance inflation factor (VIF).  And drop out variable if appropriate.
5) Do an ANOVA on the final model to determine significance of Condition and Age.