---
title: "Ordinal Model"
author: "Rong Li,Congyao Duan"
date: "2021/2/25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load("knitr","tidyverse","glmnet","car","tidyverse","ggplot2","arm","rstanarm", "magrittr", "brant")
```

## R Markdown

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
require("knitr")
opts_knit$set(root.dir = "C:/User/rong.li/Desktop/新建文件夹/MA676")
library(dplyr)
library(plyr)
```

## Code to create AC_df, the combined data.frame with all variables that we are investigating

```{r echo=FALSE}

#Change working directory to your own

setwd("C:/Users/rong.li/Desktop/新建文件夹/MA676")

adult <- read.csv("EarthAgency_Adults_R.csv", header = TRUE)

children <- read.csv("EarthAgency_Children_R.csv", header = TRUE)



adult_df <- adult %>%

  dplyr::select(

    Condition,

    Agency_Language,

    SRFactsTotal,

    invitalscore,

    inpsychscore,

    MeanSever,

    BioJtscore,

    AntJtscore,

    BioJFtotal,

    FirstLang,

    Age

  ) %>%

  mutate(

    Condition = as.factor(Condition),

    SRFactsTotal = as.integer(SRFactsTotal),

    invitalscore = as.integer(invitalscore),

    inpsychscore = as.integer(inpsychscore),

    Agency_Language = as.factor(Agency_Language),

    FirstLang = as.factor(FirstLang),

    Age

  )







#compress scores to match invitalscore and inpsychscore for children

adult_df$invitalscore[which(adult_df$invitalscore==0 | adult_df$invitalscore==1)]<-0

adult_df$invitalscore[which(adult_df$invitalscore==2) ]<-1

adult_df$invitalscore[which(adult_df$invitalscore==3) ]<-2

adult_df$invitalscore[which(adult_df$invitalscore==4 | adult_df$invitalscore==5)]<-3



adult_df$inpsychscore[which(adult_df$inpsychscore==2 | adult_df$inpsychscore==3)]<-2

adult_df$inpsychscore[which(adult_df$inpsychscore==4)]<-3

adult_df$inpsychscore[which(adult_df$inpsychscore==5)]<-4



child_df <- children %>%

  dplyr::select(

    Condition,

    Agency_Language,

    SRFactsTotal,

    invitalscore,

    inpsychscore,

    MeanSever,

    BioJtscore,

    AntJtscore,

    BioJFtotal,

    Age

  ) %>%

  mutate(

    Condition = as.factor(Condition),

    SRFactsTotal = as.integer(SRFactsTotal),

    invitalscore = as.integer(invitalscore),

    inpsychscore = as.integer(inpsychscore),

    Agency_Language = as.factor(Agency_Language),

    Age 

  )



#We're not sure we have the coding for FirstLang correct (1 = speaking their first language??)

FirstLang <- rep(1, nrow(child_df))

child_df <- child_df %>% 

  mutate(

    FirstLang = as.factor(FirstLang),

    )



#To take care of the one errant entry, children[87] (mean severity scores are divided by 4 so .67 is not possible…)

child_df$MeanSever[child_df$MeanSever==2.67] <- 2.5



#To remove children[41] which has no BIoJtscore or AntJtscore

#To remove children[45] which has no Agency_Language or SRFactsTotal

child_df <- na.omit(child_df)



## COMBINING children and adult into one data.frame

AC_df <- rbind(adult_df, child_df)



#Giving factor levels cleaner language

AC_df$Condition <- revalue(AC_df$Condition, c("1"="Obj", "2"="Nat", "3"="Per"))

AC_df$Agency_Language <- revalue(AC_df$Agency_Language, c("0"="Obj", "2"="Nat", "3"="Per"))

AC_df$Age <- ifelse(AC_df$Age > 10, "Adult", "Child")

AC_df$Age <- factor(AC_df$Age)

```

## Tasks

1) Verify the data decisions (with Lizette?) that are noted in the code chunk above.  

2) Fit the polr() model for each of the four dependent variables (MeanSever, BioJtscore, AntJtscore, BioJFtotal), using the independent variables (Condition, Agency_Language, SRFactsTotal, invitalscore, inpsychscore, FirstLang, Age)

3) Fit a linear regression model using same variables, and compare to the polr() model.  If it's comprable, then the interprebility of the linear model would argue for using it.

4) Check for multicollinearity in the models using the variance inflation factor (VIF).  And drop out variable if appropriate.

5) Do an ANOVA on the final model to determine significance of Condition and Age.

# Ordinal model
```{r}
#Meansever
AC_df$MeanSever <- factor(AC_df$MeanSever, ordered = TRUE)

plor.fit1 <- polr(MeanSever ~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
summary(plor.fit1)

#Get p-value
ctable <- coef(summary(plor.fit1))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = p)
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit1)
n <- table(AC_df$MeanSever, fitted)
percantage <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]), n[4,4]/sum(n[4,]), n[5,5]/sum(n[5,]), n[6,6]/sum(n[6,]), n[7,7]/sum(n[7,]), n[8,8]/sum(n[8,]), n[9,9]/sum(n[9,]), n[10,10]/sum(n[10,]), n[11,11]/sum(n[11,]), n[12,12]/sum(n[12,]), n[13,13]/sum(n[13,]))
rbind(n,percantage)
ME <- mean(as.character(AC_df$MeanSever) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```

```{r}
#Meansever with Combination
AC_df$comMeanSever <- AC_df$MeanSever
AC_df$comMeanSever[which((AC_df$MeanSever == 1.5))]<-1.25
AC_df$comMeanSever[which((AC_df$MeanSever == 1.75))]<-1.25
AC_df$comMeanSever[which((AC_df$MeanSever == 2))]<-1.25
AC_df$comMeanSever[which((AC_df$MeanSever == 2.25))]<-1.25
AC_df$comMeanSever <- factor(AC_df$comMeanSever, ordered = TRUE)

plor.fit1c <- polr(comMeanSever ~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
summary(plor.fit1c)

#Get p-value
ctable <- coef(summary(plor.fit1c))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = p)
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit1c)
n <- table(AC_df$comMeanSever, fitted)
percantage <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]), n[4,4]/sum(n[4,]), n[5,5]/sum(n[5,]), n[6,6]/sum(n[6,]), n[7,7]/sum(n[7,]), n[8,8]/sum(n[8,]), n[9,9]/sum(n[9,]))
rbind(n,percantage)
ME <- mean(as.character(AC_df$comMeanSever) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```


```{r}
#BioJtscore
AC_df$BioJtscore <- factor(AC_df$BioJtscore, levels = c("0","1","2","3","4"),ordered = TRUE)

plor.fit2 <- polr(BioJtscore ~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
summary(plor.fit2)

#Get p-value
ctable <- coef(summary(plor.fit2))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = p)
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit2)
n <- table(AC_df$BioJtscore, fitted)
percantage <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]), n[4,4]/sum(n[4,]), n[5,5]/sum(n[5,]))
rbind(n,percantage)
ME <- mean(as.character(AC_df$BioJtscore) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```


```{r}
#BioJtscore with Combination
AC_df$comBioJtscore<-AC_df$BioJtscore
AC_df$comBioJtscore[which((AC_df$comBioJtscore==2))]<-1
AC_df$comBioJtscore<- factor(AC_df$comBioJtscore, levels = c("0","1","3","4"),ordered = TRUE)

plor.fit2c <- polr(comBioJtscore ~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
summary(plor.fit2c)

#Get p-value
ctable <- coef(summary(plor.fit2c))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = p)
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit2c)
n <- table(AC_df$comBioJtscore, fitted)
percantage <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]), n[4,4]/sum(n[4,]))
rbind(n,percantage)
ME <- mean(as.character(AC_df$comBioJtscore) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```



```{r}
#AntJtscore
AC_df$AntJtscore <- factor(AC_df$AntJtscore, levels = c("0","1","2","3","4"),ordered = TRUE)

plor.fit3<- polr(AntJtscore~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
summary(plor.fit3)

#Get p-value
ctable <- coef(summary(plor.fit3))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = p)
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit3)
n <- table(AC_df$AntJtscore, fitted)
percantage <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]), n[4,4]/sum(n[4,]), n[5,5]/sum(n[5,]))
rbind(n,percantage)
ME <- mean(as.character(AC_df$AntJtscore) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```


```{r}
#AntJtscore with Combination
AC_df$comAntJtscore<-AC_df$AntJtscore
AC_df$comAntJtscore[which((AC_df$comAntJtscore==2))]<-1
AC_df$comAntJtscore<- factor(AC_df$comAntJtscore, levels = c("0","1","3","4"),ordered = TRUE)

plor.fit3c<- polr(comAntJtscore~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
summary(plor.fit3c)

#Get p-value
ctable <- coef(summary(plor.fit3c))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = p)
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit3c)
n <- table(AC_df$comAntJtscore, fitted)
percantage <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]), n[4,4]/sum(n[4,]))
rbind(n,percantage)
ME <- mean(as.character(AC_df$comAntJtscore) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```

```{r}
#BioJFtotal
AC_df$BioJFtotal <- factor(AC_df$BioJFtotal, levels = c("0","1","2","3","4"),ordered = TRUE)

plor.fit4 <- polr(BioJFtotal ~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
summary(plor.fit4)

#Get p-value
ctable <- coef(summary(plor.fit4))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = p)
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit4)
n <- table(AC_df$BioJFtotal, fitted)
percantage <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]), n[4,4]/sum(n[4,]), n[5,5]/sum(n[5,]))
rbind(n,percantage)
ME <- mean(as.character(AC_df$BioJFtotal) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```

```{r}
#BioJFtotal with Combination
AC_df$comBioJFtotal<-AC_df$BioJFtotal
AC_df$comBioJFtotal[which((AC_df$comBioJFtotal==3))]<-2
AC_df$comBioJFtotal<- factor(AC_df$comBioJFtotal, levels = c("0","1","2","4"),ordered = TRUE)

plor.fit4c <- polr(comBioJFtotal ~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
summary(plor.fit4c)

#Get p-value
ctable <- coef(summary(plor.fit4c))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = p)
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit4c)
n <- table(AC_df$comBioJFtotal, fitted)
percantage <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]), n[4,4]/sum(n[4,]))
rbind(n,percantage)
ME <- mean(as.character(AC_df$comBioJFtotal) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```