---
title: "Ordinal Model"
author: "Rong Li,Congyao Duan"
date: "2021/2/25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load("knitr","tidyverse","glmnet","car","tidyverse","ggplot2","arm","rstanarm", "magrittr", "brant", "regclass", "plyr")
```

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
require("knitr")
library(dplyr)
library(plyr)
```

# Code to create AC_df, the combined data.frame with all variables that we are investigating  
```{r echo=FALSE}


adult <- read.csv("EarthAgency_Adults_R.csv", header = TRUE)

children <- read.csv("EarthAgency_Children_R.csv", header = TRUE)



adult_df <- adult %>%

  dplyr::select(

    Condition,

    Agency_Language,

    SRFactsTotal,

    invitalscore,

    inpsychscore,

    MeanSever,

    BioJtscore,

    AntJtscore,

    BioJFtotal,

    FirstLang,

    Age

  ) %>%

  mutate(

    Condition = as.factor(Condition),

    SRFactsTotal = as.integer(SRFactsTotal),

    invitalscore = as.integer(invitalscore),

    inpsychscore = as.integer(inpsychscore),

    Agency_Language = as.factor(Agency_Language),

    FirstLang = as.factor(FirstLang),

    Age

  )







#compress scores to match invitalscore and inpsychscore for children

adult_df$invitalscore[which(adult_df$invitalscore==0 | adult_df$invitalscore==1)]<-0

adult_df$invitalscore[which(adult_df$invitalscore==2) ]<-1

adult_df$invitalscore[which(adult_df$invitalscore==3) ]<-2

adult_df$invitalscore[which(adult_df$invitalscore==4 | adult_df$invitalscore==5)]<-3



adult_df$inpsychscore[which(adult_df$inpsychscore==2 | adult_df$inpsychscore==3)]<-2

adult_df$inpsychscore[which(adult_df$inpsychscore==4)]<-3

adult_df$inpsychscore[which(adult_df$inpsychscore==5)]<-4



child_df <- children %>%

  dplyr::select(

    Condition,

    Agency_Language,

    SRFactsTotal,

    invitalscore,

    inpsychscore,

    MeanSever,

    BioJtscore,

    AntJtscore,

    BioJFtotal,

    Age

  ) %>%

  mutate(

    Condition = as.factor(Condition),

    SRFactsTotal = as.integer(SRFactsTotal),

    invitalscore = as.integer(invitalscore),

    inpsychscore = as.integer(inpsychscore),

    Agency_Language = as.factor(Agency_Language),

    Age 

  )



#We're not sure we have the coding for FirstLang correct (1 = speaking their first language??)

FirstLang <- rep(1, nrow(child_df))

child_df <- child_df %>% 

  mutate(

    FirstLang = as.factor(FirstLang),

    )



#To take care of the one errant entry, children[87] (mean severity scores are divided by 4 so .67 is not possible…)

child_df$MeanSever[child_df$MeanSever==2.67] <- 2.5



#To remove children[41] which has no BIoJtscore or AntJtscore

#To remove children[45] which has no Agency_Language or SRFactsTotal

child_df <- na.omit(child_df)



## COMBINING children and adult into one data.frame

AC_df <- rbind(adult_df, child_df)



#Giving factor levels cleaner language

AC_df$Condition <- revalue(AC_df$Condition, c("1"="Obj", "2"="Nat", "3"="Per"))

AC_df$Agency_Language <- revalue(AC_df$Agency_Language, c("0"="Obj", "2"="Nat", "3"="Per"))

AC_df$Age <- ifelse(AC_df$Age > 10, "Adult", "Child")

AC_df$Age <- factor(AC_df$Age)


#To check for correlation among independent variables
AC_indep <- AC_df %>%
  dplyr::select(
    Condition,
    Agency_Language,
    SRFactsTotal,
    invitalscore,
    inpsychscore,
    FirstLang,
    Age)

polycor::hetcor(AC_indep)

#note the strong correlation between Condition and Agency_Language

```

## Tasks

1) Verify the data decisions (with Lizette?) that are noted in the code chunk above.  

2) Fit the polr() model for each of the four dependent variables (MeanSever, BioJtscore, AntJtscore, BioJFtotal), using the independent variables (Condition, Agency_Language, SRFactsTotal, invitalscore, inpsychscore, FirstLang, Age)

3) Fit a linear regression model using same variables, and compare to the polr() model.  If it's comprable, then the interprebility of the linear model would argue for using it.

4) Check for multicollinearity in the models using the variance inflation factor (VIF).  And drop out variable if appropriate.

5) Do an ANOVA on the final model to determine significance of Condition and Age.


# 1.1 Mean Severity Ordinal model
```{r message=FALSE}
#Meansever
AC_df$MeanSever <- factor(AC_df$MeanSever, ordered = TRUE)

plor.fit1 <- polr(MeanSever ~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
#summary(plor.fit1)

#Get p-value
ctable <- round(coef(summary(plor.fit1)), 3)
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = round(p, 3))
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit1)
n <- table(AC_df$MeanSever, fitted)
prop.correct <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]), n[4,4]/sum(n[4,]), n[5,5]/sum(n[5,]), n[6,6]/sum(n[6,]), n[7,7]/sum(n[7,]), n[8,8]/sum(n[8,]), n[9,9]/sum(n[9,]), n[10,10]/sum(n[10,]), n[11,11]/sum(n[11,]), n[12,12]/sum(n[12,]), n[13,13]/sum(n[13,]))
prop.correct <- round(100*prop.correct, 0)
rbind(n,prop.correct)
ME <- mean(as.character(AC_df$MeanSever) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```

# 1.2 Mean Severity Ordinal model with combined levels
```{r message=FALSE}
#Meansever with Combination
AC_df$comMeanSever <- AC_df$MeanSever
AC_df$comMeanSever[which((AC_df$MeanSever == 1.5))]<-1.25
AC_df$comMeanSever[which((AC_df$MeanSever == 1.75))]<-1.25
AC_df$comMeanSever[which((AC_df$MeanSever == 2))]<-1.25
AC_df$comMeanSever[which((AC_df$MeanSever == 2.25))]<-1.25
AC_df$comMeanSever <- factor(AC_df$comMeanSever, ordered = TRUE)

plor.fit1c <- polr(comMeanSever ~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
#summary(plor.fit1c)

#Get p-value
ctable <- round(coef(summary(plor.fit1c)), 3)
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" =round(p, 3))
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit1c)
n <- table(AC_df$comMeanSever, fitted)
prop.correct <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]), n[4,4]/sum(n[4,]), n[5,5]/sum(n[5,]), n[6,6]/sum(n[6,]), n[7,7]/sum(n[7,]), n[8,8]/sum(n[8,]), n[9,9]/sum(n[9,]))
prop.correct <- round(100*prop.correct, 0)
rbind(n,prop.correct)
ME <- mean(as.character(AC_df$comMeanSever) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```

# 1.3 Mean Severity Ordinal model with combined levels (bcm)
```{r message=FALSE}
#Meansever combined into three levels (bcm)
AC_df$comMeanSever <- AC_df$MeanSever
AC_df$comMeanSever[which((AC_df$MeanSever < 1.5))]<-1
AC_df$comMeanSever[which((AC_df$MeanSever > 1.25 & AC_df$MeanSever < 2.25))]<-2
AC_df$comMeanSever[which((AC_df$MeanSever > 2))]<-3
AC_df$comMeanSever <- factor(AC_df$comMeanSever, ordered = TRUE)

table(AC_df$MeanSever)
table(AC_df$comMeanSever)

plor.fit1c <- polr(comMeanSever ~  Condition + Agency_Language + SRFactsTotal + invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
#summary(plor.fit1c)

#Get p-value
ctable <- round(coef(summary(plor.fit1c)), 3)
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" =round(p, 3))
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit1c)
n <- table(AC_df$comMeanSever, fitted)
prop.correct <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]))
prop.correct <- round(100*prop.correct, 0)
rbind(n,prop.correct)
ME <- mean(as.character(AC_df$comMeanSever) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```

# 2.1 Biocentric Justification score, Ordinal model
```{r message=FALSE}
#BioJtscore
AC_df$BioJtscore <- factor(AC_df$BioJtscore, levels = c("0","1","2","3","4"),ordered = TRUE)

plor.fit2 <- polr(BioJtscore ~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
#summary(plor.fit2)

#Get p-value
ctable <- round(coef(summary(plor.fit2)), 3)
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = round(p, 3))
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit2)
n <- table(AC_df$BioJtscore, fitted)
prop.correct <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]), n[4,4]/sum(n[4,]), n[5,5]/sum(n[5,]))
prop.correct <- round(100*prop.correct, 0)
rbind(n,prop.correct)
ME <- mean(as.character(AC_df$BioJtscore) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```

# 2.2 Biocentric Justification score, Ordinal model with combined levels
```{r message=FALSE}
#BioJtscore with Combination
AC_df$comBioJtscore<-AC_df$BioJtscore
AC_df$comBioJtscore[which((AC_df$comBioJtscore==2))]<-1
AC_df$comBioJtscore<- factor(AC_df$comBioJtscore, levels = c("0","1","3","4"),ordered = TRUE)

plor.fit2c <- polr(comBioJtscore ~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
#summary(plor.fit2c)

#Get p-value
ctable <- round(coef(summary(plor.fit2c)), 3)
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = round(p, 3))
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit2c)
n <- table(AC_df$comBioJtscore, fitted)
prop.correct <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]), n[4,4]/sum(n[4,]))
prop.correct <- round(100*prop.correct, 0)
rbind(n,prop.correct)
ME <- mean(as.character(AC_df$comBioJtscore) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```

# 2.3 Biocentric Justification score, Ordinal model with combined levels (bcm)
```{r message=FALSE}
#BioJtscore with Combination (bcm)
AC_df$comBioJtscore<-AC_df$BioJtscore
AC_df$comBioJtscore[which((AC_df$comBioJtscore==0))]<-1
AC_df$comBioJtscore[which((AC_df$comBioJtscore==2))]<-1
AC_df$comBioJtscore[which((AC_df$comBioJtscore==3))]<-2
AC_df$comBioJtscore[which((AC_df$comBioJtscore==4))]<-3
AC_df$comBioJtscore<- factor(AC_df$comBioJtscore, ordered = TRUE)

table(AC_df$BioJtscore)
table(AC_df$comBioJtscore)

plor.fit2c <- polr(comBioJtscore ~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
#summary(plor.fit2c)

#Get p-value
ctable <- round(coef(summary(plor.fit2c)), 3)
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = round(p, 3))
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit2c)
n <- table(AC_df$comBioJtscore, fitted)
prop.correct <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]))
prop.correct <- round(100*prop.correct, 0)
rbind(n,prop.correct)
ME <- mean(as.character(AC_df$comBioJtscore) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```

# 3.1 Anthropocentric Justification score, Ordinal model
```{r message=FALSE}
#AntJtscore
AC_df$AntJtscore <- factor(AC_df$AntJtscore, levels = c("0","1","2","3","4"),ordered = TRUE)

plor.fit3<- polr(AntJtscore~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
#summary(plor.fit3)

#Get p-value
ctable <- round(coef(summary(plor.fit3)), 3)
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = round(p, 3))
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit3)
n <- table(AC_df$AntJtscore, fitted)
prop.correct <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]), n[4,4]/sum(n[4,]), n[5,5]/sum(n[5,]))
prop.correct <- round(100*prop.correct, 0)
rbind(n,prop.correct)
ME <- mean(as.character(AC_df$AntJtscore) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```

# 3.2 Anthropocentric Justification score, Ordinal model with combined levels
```{r message=FALSE}
#AntJtscore with Combination
AC_df$comAntJtscore<-AC_df$AntJtscore
AC_df$comAntJtscore[which((AC_df$comAntJtscore==2))]<-1
AC_df$comAntJtscore<- factor(AC_df$comAntJtscore, levels = c("0","1","3","4"),ordered = TRUE)

plor.fit3c<- polr(comAntJtscore~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
#summary(plor.fit3c)

#Get p-value
ctable <- round(coef(summary(plor.fit3c)), 3)
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = round(p, 3))
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit3c)
n <- table(AC_df$comAntJtscore, fitted)
prop.correct <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]), n[4,4]/sum(n[4,]))
prop.correct <- round(100*prop.correct, 0)
rbind(n,prop.correct)
ME <- mean(as.character(AC_df$comAntJtscore) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```

# 3.3 Anthropocentric Justification score, Ordinal model with combined levels (bcm)
```{r message=FALSE}
#AntJtscore with Combination (bcm)
AC_df$comAntJtscore<-AC_df$AntJtscore
AC_df$comAntJtscore[which((AC_df$comAntJtscore==0))]<-1
AC_df$comAntJtscore[which((AC_df$comAntJtscore==2))]<-1
AC_df$comAntJtscore[which((AC_df$comAntJtscore==3))]<-2
AC_df$comAntJtscore[which((AC_df$comAntJtscore==4))]<-3
AC_df$comAntJtscore<- factor(AC_df$comAntJtscore, ordered = TRUE)

table(AC_df$AntJtscore)
table(AC_df$comAntJtscore)

plor.fit3c<- polr(comAntJtscore~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
#summary(plor.fit3c)

#Get p-value
ctable <- round(coef(summary(plor.fit3c)), 3)
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = round(p, 3))
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit3c)
n <- table(AC_df$comAntJtscore, fitted)
prop.correct <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]))
prop.correct <- round(100*prop.correct, 0)
rbind(n,prop.correct)
ME <- mean(as.character(AC_df$comAntJtscore) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```

# 4.1 Biocentric choice score, Ordinal model
```{r message=FALSE}
#BioJFtotal
AC_df$BioJFtotal <- factor(AC_df$BioJFtotal, levels = c("0","1","2","3","4"),ordered = TRUE)

plor.fit4 <- polr(BioJFtotal ~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
#summary(plor.fit4)

#Get p-value
ctable <- round(coef(summary(plor.fit4)), 3)
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = round(p, 3))
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit4)
n <- table(AC_df$BioJFtotal, fitted)
prop.correct <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]), n[4,4]/sum(n[4,]), n[5,5]/sum(n[5,]))
prop.correct <- round(100*prop.correct, 0)
rbind(n,prop.correct)
ME <- mean(as.character(AC_df$BioJFtotal) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```

# 4.2 Biocentric choice score, Ordinal model with combined levels
```{r message=FALSE}
#BioJFtotal with Combination
AC_df$comBioJFtotal<-AC_df$BioJFtotal
AC_df$comBioJFtotal[which((AC_df$comBioJFtotal==3))]<-2
AC_df$comBioJFtotal<- factor(AC_df$comBioJFtotal, levels = c("0","1","2","4"),ordered = TRUE)

plor.fit4c <- polr(comBioJFtotal ~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
#summary(plor.fit4c)

#Get p-value
ctable <- round(coef(summary(plor.fit4c)), 3)
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = round(p, 3))
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit4c)
n <- table(AC_df$comBioJFtotal, fitted)
prop.correct <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]), n[4,4]/sum(n[4,]))
prop.correct <- round(100*prop.correct, 0)
rbind(n,prop.correct)
ME <- mean(as.character(AC_df$comBioJFtotal) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```

# 4.3 Biocentric choice score, Ordinal model with combined levels (bcm)
```{r message=FALSE}
#BioJFtotal with Combination
AC_df$comBioJFtotal<-AC_df$BioJFtotal
AC_df$comBioJFtotal[which((AC_df$comBioJFtotal==0))]<-1
#AC_df$comBioJFtotal[which((AC_df$comBioJFtotal==2))]<-1
#AC_df$comBioJFtotal[which((AC_df$comBioJFtotal==3))]<-2
AC_df$comBioJFtotal[which((AC_df$comBioJFtotal==4))]<-3
AC_df$comBioJFtotal<- factor(AC_df$comBioJFtotal, ordered = TRUE)

table(AC_df$BioJFtotal)
table(AC_df$comBioJFtotal)

plor.fit4c <- polr(comBioJFtotal ~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
#summary(plor.fit4c)

#Get p-value
ctable <- round(coef(summary(plor.fit4c)), 3)
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = round(p, 3))
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit4c)
n <- table(AC_df$comBioJFtotal, fitted)
prop.correct <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]))
prop.correct <- round(100*prop.correct, 0)
rbind(n,prop.correct)
ME <- mean(as.character(AC_df$comBioJFtotal) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```

# 5.1 Linear Regression
```{r}
lm.fit1 <- lm(MeanSever ~ Condition + Agency_Language + 
                SRFactsTotal + invitalscore + inpsychscore + FirstLang + Age, data = AC_df)

summary(lm.fit1)

lm.fit2 <- lm(BioJtscore ~ Condition + Agency_Language + 
                SRFactsTotal + invitalscore + inpsychscore + FirstLang + Age, data = AC_df)

summary(lm.fit2)

lm.fit3 <- lm(AntJtscore ~ Condition + Agency_Language + 
                SRFactsTotal + invitalscore + inpsychscore + FirstLang + Age, data = AC_df)

summary(lm.fit3)

lm.fit4 <- lm(BioJFtotal ~ Condition + Agency_Language + 
                SRFactsTotal + invitalscore + inpsychscore + FirstLang + Age, data = AC_df)

summary(lm.fit4)


```

# 5.2 Binned Residual Plots
```{r}
binnedplot(fitted(lm.fit1),resid(lm.fit1))
binnedplot(fitted(lm.fit2),resid(lm.fit2))
binnedplot(fitted(lm.fit3),resid(lm.fit3))
binnedplot(fitted(lm.fit4),resid(lm.fit4))
```

# 5.3 Multicollinearity Check using VIF
```{r}
VIF(lm.fit1)
VIF(lm.fit2)
VIF(lm.fit3)
VIF(lm.fit4)
```

# 5.4 Anova test comparing Age
```{r}
#Mean Severity
plor.fit1c2 <- polr(comMeanSever ~  Condition + Agency_Language + SRFactsTotal + invitalscore  + inpsychscore + FirstLang, data = AC_df)

anova(plor.fit1c, plor.fit1c2)


#Biocentric Justification score
plor.fit2c2 <- polr(comBioJtscore ~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang, data = AC_df)

anova(plor.fit2c, plor.fit2c2)


#Anthropocentric Justification score
plor.fit3c2<- polr(comAntJtscore~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang, data = AC_df)

anova(plor.fit3c,plor.fit3c2)


#Biocentric choice score
plor.fit4c2 <- polr(comBioJFtotal ~  Condition + Agency_Language + SRFactsTotal +invitalscore  + inpsychscore + FirstLang, data = AC_df)

anova(plor.fit4c,plor.fit4c2)
```