---
title: "Earth Agency Project: Progress Report"
author: "Consulting Team A, group 3"
date: "March 14th, 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load("knitr","tidyverse","glmnet","car","tidyverse","ggplot2","arm","rstanarm", "magrittr", "brant", "plyr", "gplots", "gridExtra")
```
   
# 1. Decisions made in creating the working data frame
  
  (a) We have combined *EarthAgency_Adults_R.csv* and *EarthAgency_Children_R.csv* into one data.frame: `AC_df`.  We have done this so that we can make an Adult vs. children comparison.  To combined the two data sets we have done b-d.
  
  (b) To normalize the adult and children's `invitalscores`, we have compressed the adult's scores (which ranged from 0-5), to match the children's scores (which ranged from 0-3).  
``` {r echo=FALSE, message=FALSE, warning=FALSE}
b <- data.frame(original=as.character(seq(0, 5)), normalized=as.character(c(0,0,1,2,3,3)))
kable(t(b))  
```
  
  (c) To normalize the adult and children's `inpsychscore`, we have compressed the adult's scores (which ranged from 0-5), to match the children's scores (which ranged from 0-4).  
``` {r echo=FALSE, message=FALSE, warning=FALSE}
c <- data.frame(original=as.character(seq(0, 5)), normalized=as.character(c(0,1,2,2,3,3)))
kable(t(c))  
```
  
 (d) We have added `FirstLang` to the children's records, and assigned every child a value of 1 for `FirstLang`.  We're assuming that 1=using first language, and 0=not using first language.    
  
 (e) The 87th entry in the children's record's has a `MeanSeverity` of 2.67.  But 2.67 is not a possible value (given that `MeanSeverity` is an average of 4 integer scores, and should thus be a multiple of 0.25).  We've changed the `MeanSeverity` for that record to 2.5.  
  
 (f) The 41st children's record has no `BIoJtscore` or `AntJtscore`.  We did not use this record in the data.frame.  
  
 (g) The 45th children's record has no `Agency_Language` or `SRFactsTotal`.  We did not use this record in the data.frame.
 
 (h) We have not included the independent variable `SRTotal` in the data frame.  Our understanding is that this variable is measuring comprehension of the video and was designed to test if children had payed attention to the video.  For the children it was a 4 question test.  Of the 91 children, 4 had a score of 2, 28 a score of 3, and 59 a score of 4.  And we have not filtered out any children from the data frame based on this comprehension check.  
\newpage
 (i) There is also a `SRTotal` variable for the adults.  We did not include it in the data frame.  If it is also a comprehension check, it might be useful consider filtering out some of the adults based on the results.  This is a table of the results:
``` {r echo=FALSE, message=FALSE, warning=FALSE}
k <- data.frame(score=as.character(seq(6, 12)), count=as.character(c(1,1,15,18,40,37,20)))
kable(t(k))
```
 
  (j) We have renamed the `Condition` levels to `Obj` (object), `Nat` (nature, animal, vitalist), `Per` (person, psychological), for ease of understanding and consistency while we were coding.  
  
  (k) For a better model fit, we have combined the original 13 levels of `MeanSeverity` into three levels, as follows:  
``` {r echo=FALSE, message=FALSE, warning=FALSE}
k <- data.frame(original=as.character(format(round(seq(0, 3, .25), 3))), combined=as.character(c(1,1,1,1,1,1,2,2,2,3,3,3,3)))
kable(t(k), align="c")
```
  
  (l) For a better model fit, we have combined the original 5 levels of `BioJtscore` (the number of scenarios where the respondent used a biocentric justification), into three levels, as follows:  
``` {r echo=FALSE, message=FALSE, warning=FALSE}
l <- data.frame(original=as.character(seq(0, 4)), combined=as.character(c(1,1,1,2,3)))
kable(t(l))  
```
  
  (m) For a better model fit, we have combined the original 5 levels of `AntJtscore` (the number of scenarios where the respondent used an anthropocentric justification), into three levels, as follows:  
``` {r echo=FALSE, message=FALSE, warning=FALSE}
m <- data.frame(original=as.character(seq(0, 4)), combined=as.character(c(1,1,1,2,3)))
kable(t(m))  
```
  
  (n) For a better model fit, we have combined the original 5 levels of `BioJFtotal` (the number of scenarios where the respondent chose biocentric when given a choice between biocentric and anthropocentric), into three levels, as follows:  
``` {r echo=FALSE, message=FALSE, warning=FALSE}
n <- data.frame(original=as.character(seq(0, 4)), combined=as.character(c(1,1,2,3,3)))
kable(t(n))  
```
  
```{r echo=FALSE}
#Change working directory to your own
setwd("~/MSSP/Consulting/EarthAgencyProject")

adult <- read.csv("EarthAgency_Adults_R.csv", header = TRUE)
children <- read.csv("EarthAgency_Children_R.csv", header = TRUE)
```

```{r echo=FALSE}
adult_df <- adult %>%
  dplyr::select(
    Condition,
    Agency_Language,
    SRFactsTotal,
    invitalscore,
    inpsychscore,
    MeanSever,
    BioJtscore,
    AntJtscore,
    BioJFtotal,
    FirstLang,
    Age
  ) %>%
  mutate(
    Condition = as.factor(Condition),
    SRFactsTotal = as.integer(SRFactsTotal),
    invitalscore = as.integer(invitalscore),
    inpsychscore = as.integer(inpsychscore),
    Agency_Language = as.factor(Agency_Language),
    FirstLang = as.factor(FirstLang),
    Age
  )

#compress scores to match invitalscore and inpsychscore for children

adult_df$invitalscore[which(adult_df$invitalscore==0 | adult_df$invitalscore==1)]<-0
adult_df$invitalscore[which(adult_df$invitalscore==2) ]<-1
adult_df$invitalscore[which(adult_df$invitalscore==3) ]<-2
adult_df$invitalscore[which(adult_df$invitalscore==4 | adult_df$invitalscore==5)]<-3

adult_df$inpsychscore[which(adult_df$inpsychscore==2 | adult_df$inpsychscore==3)]<-2
adult_df$inpsychscore[which(adult_df$inpsychscore==4)]<-3
adult_df$inpsychscore[which(adult_df$inpsychscore==5)]<-4

child_df <- children %>%
  dplyr::select(
    Condition,
    Agency_Language,
    SRFactsTotal,
    invitalscore,
    inpsychscore,
    MeanSever,
    BioJtscore,
    AntJtscore,
    BioJFtotal,
    Age
  ) %>%
  mutate(
    Condition = as.factor(Condition),
    SRFactsTotal = as.integer(SRFactsTotal),
    invitalscore = as.integer(invitalscore),
    inpsychscore = as.integer(inpsychscore),
    Agency_Language = as.factor(Agency_Language),
    Age 
  )

#We're not sure we have the coding for FirstLang correct (1 = speaking their first language??)
FirstLang <- rep(1, nrow(child_df))
child_df <- child_df %>% 
  mutate(
    FirstLang = as.factor(FirstLang),
    )

#To take care of the one errant entry, children[87] (mean severity scores are divided by 4 so .67 is not possible…)
child_df$MeanSever[child_df$MeanSever==2.67] <- 2.5

#To remove children[41] which has no BIoJtscore or AntJtscore
#To remove children[45] which has no Agency_Language or SRFactsTotal
child_df <- na.omit(child_df)

## COMBINING children and adult into one data.frame
AC_df <- rbind(adult_df, child_df)

#Giving factor levels cleaner language
AC_df$Condition <- revalue(AC_df$Condition, c("1"="Obj", "2"="Nat", "3"="Per"))
AC_df$Agency_Language <- revalue(AC_df$Agency_Language, c("0"="Obj", "2"="Nat", "3"="Per"))
AC_df$Age <- ifelse(AC_df$Age > 10, "Adult", "Child")
AC_df$Age <- factor(AC_df$Age)
```
\newpage
# 2. Experimental Design concerns  
The chart below shows our understanding of the variables collected.  The green are the independent variables with their levels, and the brown are the four dependent variables.  As you have noted, the flow our your experiment design has intertwined the `Condition` variable with the `Agency_language`, `inpsychscore` and `invitalscore` variables.  In particular, since the questionnaire was given after the participants watched the video, it's not clear that the `invitalscore` and `inpsychscore` variables are measuring the participants underlying beliefs, or the beliefs expressed in the video that they just watched.  Also `Agency_language`, which is attempting to measure how the participants describe the video, overlaps with the perspective of the video watched.  As such it is not clear that `Agency_language` is descriptive of the participant or of the video they just watched.  

```{r, echo=FALSE, fig.align='center'}
include_graphics("List of Variables.pdf")
```
\newpage
# 3. Correlation among independent variables   
Because of our worry about the independence of the independent variables, we checked the correlations between the independent variables.  The following chart (which is redundant across the diagonal), shows Pearson product-moment correlations between the numeric variables (`SRFactsTotal`, `invitalscore`, `inpsychscore`), a polychoric correlations between ordinal categorical variables (`Condition`, `Agency_Language`, `FirstLang` and `Age`), and polyserial correlations between numeric and ordinal variables.  1 or -1 is a strong correlation.  0 is no correlation.   
\newline
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
AC_indep <- AC_df %>%
  dplyr::select(
    Condition,
    Agency_Language,
    SRFactsTotal,
    invitalscore,
    inpsychscore,
    FirstLang,
    Age)

cor.check <- polycor::hetcor(AC_indep)
kable(round(cor.check$correlations,2))
```
  
## 3a. Correlation between `Condition` and `Agency_language`  
`Condition` and `Agency_language` had the strongest correlation and the p-value of the Pearson's chi-square test was effectively zero ($p=7.3*10^{-36}$).  Because of this, and because of our concerns about the experimental design, we have not included `Agency_language` in the model fits below.  If we have time, we will explore using PCA (principal component analysis) to combine these two independent variables.  
```{r echo=FALSE, warning=FALSE, out.width="33%"}
pvalue <- chisq.test(table(AC_df$Condition, AC_df$Agency_Language), simulate.p.value = FALSE)$p.value
balloonplot(table(AC_df$Condition, AC_df$Agency_Language), xlab ="Condition", ylab="Agency_Lang",
            label = TRUE, show.margins = TRUE, label.size=.5)

```
  
\newpage  
## 3b. Correlation between `Condition`, `invitalscore`, and `inpsychscore`  
A Chi-square test shows that there is not a significant correlation between `Condition` and `invitalscore` (p=0.54), and there is a slightly significant correlation between `Condition` and `inpsychscore` (p=0.04).  But the correlation between `invitalscore` and `inpsychscore` is highly significant ($p=5.0*10^{-4}$).  We have included both of these variables in the model fit below, and (if time permits) we are going to explore using PCA (principal component analysis) to combine these two independent variables (`invitalscore` and `inpsychsocre`).    

```{r echo=FALSE, warning=FALSE, out.width="33%"}
pvalue.1 <- chisq.test(table(AC_df$Condition, AC_df$invitalscore), simulate.p.value = FALSE)$p.value
balloonplot(table(AC_df$Condition, AC_df$invitalscore), xlab ="Condition", ylab="invitalscore",
            label = TRUE, show.margins = TRUE, label.size=.5)

pvalue.2 <- chisq.test(table(AC_df$Condition, AC_df$inpsychscore), simulate.p.value = FALSE)$p.value
balloonplot(table(AC_df$Condition, AC_df$inpsychscore), xlab ="Condition", ylab="inpsychscore",
            label = TRUE, show.margins = TRUE, label.size=.5)

pvalue.3 <- chisq.test(table(AC_df$inpsychscore, AC_df$invitalscore), simulate.p.value = TRUE)$p.value
balloonplot(table(AC_df$invitalscore, AC_df$inpsychscore), xlab ="invitalscore", ylab="inpsychscore",
            label = TRUE, show.margins = TRUE, label.size=.5)
```
  
## 3c. Correlation between `FirstLang` and `Age`  
Because we are assuming that the 89 children in the study are all using their first language, there is a strong correlation between `FirstLang` and `Age` ($p=2.4*10^{-6}$).  But, for contextual reasons, we have left both of these variables in the models below.  And when we ran the model without `FirstLang` it did not imporove the model fit.
```{r echo=FALSE, warning=FALSE, out.width="33%"}
pvalue.4 <- chisq.test(table(AC_df$FirstLang, AC_df$Age), simulate.p.value = FALSE)$p.value
balloonplot(table(AC_df$FirstLang, AC_df$Age), xlab ="First Language", ylab="Age",
            label = TRUE, show.margins = TRUE, label.size=.5)
```
```{r echo=FALSE}
## Are Condition and SRFactsTotal  correlated????  
## The ordinal regression shows more facts remembered the more likely "Per" and the less likely "Obj" (BUT it's not a really big difference in the probability of being in that particular group...).  BUT t-tests show there is no significant difference in mean SRFactsTotal between any of the combinations of "Obj", "Nat", or "Per"

##plot shows no visual correlation
#plot(AC_df$Condition, AC_df$SRFactsTotal)

##combination of t-tests shows no associatin
#t.test(AC_df$SRFactsTotal[AC_df$Condition=="Obj"], AC_df$SRFactsTotal[AC_df$Condition=="Nat"], alternative = "two.sided", var.equal = FALSE)
#t.test(AC_df$SRFactsTotal[AC_df$Condition=="Obj"], AC_df$SRFactsTotal[AC_df$Condition=="Per"], alternative = "two.sided", var.equal = FALSE)
#t.test(AC_df$SRFactsTotal[AC_df$Condition=="Per"], AC_df$SRFactsTotal[AC_df$Condition=="Nat"], alternative = "two.sided", var.equal = FALSE)

##ordinal regression shows no predictive value for SRFactsTotal - the probability for all three conditions ranges from 32% to 34% (even though there are different patterns to the probobilities within this small range)
#Condition_ordinal <- polr(Condition ~ SRFactsTotal, AC_df)
#summary(Condition_ordinal)

#plot(facts, predict(Condition_ordinal, newdata=data.frame(SRFactsTotal=facts), type="p")[,1], type='l', ylab='Prob', ylim=c(.32,.34))
  #lines(facts, predict(Condition_ordinal, newdata=data.frame(SRFactsTotal=facts), type="p")[,2], col='red')
  #lines(facts, predict(Condition_ordinal, newdata=data.frame(SRFactsTotal=facts), type="p")[,3], col='blue')
  #legend("topleft", lty=1, col=c("black", "red", "blue"), legend=c("Object", "Nature", "Person"))

##This code does the same as above - but using the logit formula - it has not been graphed, but would be graphed the same as the plot above
facts   <- seq(from=0, to=15, by=1)
xbeta <- facts*(0.003059)
logistic_cdf <- function(x) {
  return( 1/(1+exp(-x) ) )
}

p1 <- logistic_cdf( -0.6983 - xbeta )
p2 <- logistic_cdf( 0.7084 - xbeta ) - logistic_cdf( -0.6983 - xbeta )
p3 <- 1 - logistic_cdf( 0.7084 - xbeta )

```
\newpage
# 5. Modeling  
## 5a. Mean Severity Ordinal model with combined levels
```{r echo=FALSE, message=FALSE, comment=NA}
#Meansever combined into three levels
AC_df$comMeanSever <- AC_df$MeanSever
AC_df$comMeanSever[which((AC_df$MeanSever < 1.5))]<-1
AC_df$comMeanSever[which((AC_df$MeanSever > 1.25 & AC_df$MeanSever < 2.25))]<-2
AC_df$comMeanSever[which((AC_df$MeanSever > 2))]<-3
AC_df$comMeanSever <- factor(AC_df$comMeanSever, ordered = TRUE)

cat("original levels")
table(AC_df$MeanSever)
cat("combined levels")
table(AC_df$comMeanSever)

plor.fit1c <- polr(comMeanSever ~  Condition + SRFactsTotal + invitalscore  + inpsychscore + FirstLang + Age, data = AC_df)
#summary(plor.fit1c)
plor.fit1c$call

#Get p-value
ctable <- round(coef(summary(plor.fit1c)), 3)
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" =round(p, 3))
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit1c)
n <- table(AC_df$comMeanSever, fitted)
prop.correct <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]))
prop.correct <- round(100*prop.correct, 0)
rbind(n,prop.correct)
ME <- mean(as.character(AC_df$comMeanSever) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")

#misclassification error with 'FirstLang' = 0.504
#misclassification error with/out "FirstLang' = 0.5
```
\newpage

## 5b. Biocentric Justification score, Ordinal model with combined levels
```{r echo=FALSE, message=FALSE, comment=NA}
#BioJtscore with Combination
AC_df$comBioJtscore<-AC_df$BioJtscore
AC_df$comBioJtscore[which((AC_df$comBioJtscore==0))]<-1
AC_df$comBioJtscore[which((AC_df$comBioJtscore==2))]<-1
AC_df$comBioJtscore[which((AC_df$comBioJtscore==3))]<-2
AC_df$comBioJtscore[which((AC_df$comBioJtscore==4))]<-3
AC_df$comBioJtscore<- factor(AC_df$comBioJtscore, ordered = TRUE)

cat("original levels")
table(AC_df$BioJtscore)
cat("combined levels")
table(AC_df$comBioJtscore)

plor.fit2c <- polr(comBioJtscore ~  Condition + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
#summary(plor.fit2c)
plor.fit2c$call

#Get p-value
ctable <- round(coef(summary(plor.fit2c)), 3)
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = round(p, 3))
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit2c)
n <- table(AC_df$comBioJtscore, fitted)
prop.correct <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]))
prop.correct <- round(100*prop.correct, 0)
rbind(n,prop.correct)
ME <- mean(as.character(AC_df$comBioJtscore) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```
\newpage

## 5c. Anthropocentric Justification score, Ordinal model with combined levels
```{r echo=FALSE, message=FALSE, comment=NA}
#AntJtscore with Combination (bcm)
AC_df$comAntJtscore<-AC_df$AntJtscore
AC_df$comAntJtscore[which((AC_df$comAntJtscore==0))]<-1
AC_df$comAntJtscore[which((AC_df$comAntJtscore==2))]<-1
AC_df$comAntJtscore[which((AC_df$comAntJtscore==3))]<-2
AC_df$comAntJtscore[which((AC_df$comAntJtscore==4))]<-3
AC_df$comAntJtscore<- factor(AC_df$comAntJtscore, ordered = TRUE)

cat("original levels")
table(AC_df$AntJtscore)
cat("combined levels")
table(AC_df$comAntJtscore)

plor.fit3c<- polr(comAntJtscore~  Condition + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
#summary(plor.fit3c)
plor.fit3c$call

#Get p-value
ctable <- round(coef(summary(plor.fit3c)), 3)
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = round(p, 3))
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit3c)
n <- table(AC_df$comAntJtscore, fitted)
prop.correct <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]))
prop.correct <- round(100*prop.correct, 0)
rbind(n,prop.correct)
ME <- mean(as.character(AC_df$comAntJtscore) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```
\newpage

## 5d. Biocentric choice score, Ordinal model with combined levels
```{r echo=FALSE, message=FALSE, comment=NA}
#BioJFtotal with Combination
AC_df$comBioJFtotal<-AC_df$BioJFtotal
AC_df$comBioJFtotal[which((AC_df$comBioJFtotal==0))]<-1
#AC_df$comBioJFtotal[which((AC_df$comBioJFtotal==2))]<-1
#AC_df$comBioJFtotal[which((AC_df$comBioJFtotal==3))]<-2
AC_df$comBioJFtotal[which((AC_df$comBioJFtotal==4))]<-3
AC_df$comBioJFtotal<- factor(AC_df$comBioJFtotal, ordered = TRUE)

cat("original levels")
table(AC_df$BioJFtotal)
cat("combined levels")
table(AC_df$comBioJFtotal)

plor.fit4c <- polr(comBioJFtotal ~  Condition + SRFactsTotal +invitalscore  + inpsychscore + FirstLang+Age, data = AC_df)
#summary(plor.fit4c)
plor.fit4c$call

#Get p-value
ctable <- round(coef(summary(plor.fit4c)), 3)
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable1 <- cbind(ctable, "p value" = round(p, 3))
ctable1

#Compute confusion table and misclassification error
fitted <- predict(plor.fit4c)
n <- table(AC_df$comBioJFtotal, fitted)
prop.correct <- c(n[1,1]/sum(n[1,]),n[2,2]/sum(n[2,]),n[3,3]/sum(n[3,]))
prop.correct <- round(100*prop.correct, 0)
rbind(n,prop.correct)
ME <- mean(as.character(AC_df$comBioJFtotal) !=as.character(fitted))
cat("Misclassification error is:",ME,"\n")
```
\newpage
 
# 6. For `Age`, is there a significant difference in the dependent variables `MeanSeverity`, `BioJscore`, `AntJtscore`, and `BioJFtotal`?  
Yes, there is a significant difference.  

## 6a. Visualization  
You can see the difference in the plots of the dependent variables colored by `Age`.  Note: none of the other predictor variables are included in this visualization.

```{r echo=FALSE, warning=FALSE, message=FALSE}
#-----
#Calculate % in each of the MeanSeverity outcomes for children
Age1_df <- AC_df %>% 
  filter(Age=="Child") %>% 
  group_by(comMeanSever, Age) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

#Calculate % in each of the MeanSeverity outcomes for Adults
Age2_df <- AC_df %>% 
  filter(Age=="Adult") %>% 
  group_by(comMeanSever, Age) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

Age_df <- bind_rows(Age1_df, Age2_df)

gg.1 <- ggplot(Age_df, aes(x=comMeanSever, y=prop, fill=Age)) +
  geom_col(color="white", position = position_dodge2(width = 0.001, preserve = "single")) +
  labs(x="score", y="proportion") +
  coord_cartesian(ylim=c(0, 1), xlim=c(1,3)) +
  theme_minimal(base_size=8) +
  labs(title="Mean Severity for each Age") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))

#-----
#Calculate % in each of the comBioJtscore outcomes for children
Age1_df <- AC_df %>% 
  filter(Age=="Child") %>% 
  group_by(comBioJtscore, Age) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

#Calculate % in each of the comBioJtscore outcomes for Adults
Age2_df <- AC_df %>% 
  filter(Age=="Adult") %>% 
  group_by(comBioJtscore, Age) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

Age_df <- bind_rows(Age1_df, Age2_df)

gg.2 <- ggplot(Age_df, aes(x=comBioJtscore, y=prop, fill=Age)) +
  geom_col(color="white", position = position_dodge2(width = 0.001, preserve = "single")) +
  labs(x="score", y="proportion") +
  coord_cartesian(ylim=c(0, 1), xlim=c(1,3)) +
  theme_minimal(base_size=8) +
  theme(legend.position="none") +
  labs(title="Biocentric Justification for each Age") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))

#-----
#Calculate % in each of the comAntJtscore outcomes for children
Age1_df <- AC_df %>% 
  filter(Age=="Child") %>% 
  group_by(comAntJtscore, Age) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

#Calculate % in each of the comAntJtscore outcomes for Adults
Age2_df <- AC_df %>% 
  filter(Age=="Adult") %>% 
  group_by(comAntJtscore, Age) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

Age_df <- bind_rows(Age1_df, Age2_df)

gg.3 <- ggplot(Age_df, aes(x=comAntJtscore, y=prop, fill=Age)) +
  geom_col(color="white", position = position_dodge2(width = 0.001, preserve = "single")) +
  labs(x="score", y="proportion") +
  coord_cartesian(ylim=c(0, 1), xlim=c(1,3)) +
  theme_minimal(base_size=8) +
  theme(legend.position="none") +
  labs(title="Anthropocentric Justification for each Age") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))

#-----
#Calculate % in each of the comBioJFtotal outcomes for children
Age1_df <- AC_df %>% 
  filter(Age=="Child") %>% 
  group_by(comBioJFtotal, Age) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

#Calculate % in each of the comBioJFtotal outcomes for Adults
Age2_df <- AC_df %>% 
  filter(Age=="Adult") %>% 
  group_by(comBioJFtotal, Age) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

Age_df <- bind_rows(Age1_df, Age2_df)

gg.4 <- ggplot(Age_df, aes(x=comBioJFtotal, y=prop, fill=Age)) +
  geom_col(color="white", position = position_dodge2(width = 0.001, preserve = "single")) +
  labs(x="score", y="proportion") +
  coord_cartesian(ylim=c(0, 1), xlim=c(1,3)) +
  theme_minimal(base_size=8) +
  theme(legend.position="none") +
  labs(title="Biocentric Choice for each Age") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))

grid.arrange(gg.1, gg.2, gg.3, gg.4, ncol=2)
```
\newpage
 
## 6b. ANOVA test  
We did an ANOVA test using our ordinal models and found that when Age was included in the model there was significant difference from the model that excluded Age.  Which means that knowing the age of the participant (adult vs. child) makes a difference to the modeling, and thus there is a significant difference between the dependent variable scores for adults and children.  The p-values for these differences are `MeanSeverity` ($p=4.8*10^{-09}$), `BioJscore` ($p=5.3*10^{-08}$), `AntJtscore` ($p=1.8*10^{-04}$), and `BioJFtotal` ($p=0.015$).
```{r echo=FALSE, comment=NA}
#Mean Severity
plor.fit1c2 <- polr(comMeanSever ~  Condition +  SRFactsTotal + invitalscore  + inpsychscore + FirstLang, data = AC_df)

anova(plor.fit1c, plor.fit1c2)


#Biocentric Justification score
plor.fit2c2 <- polr(comBioJtscore ~  Condition +  SRFactsTotal +invitalscore  + inpsychscore + FirstLang, data = AC_df)

anova(plor.fit2c, plor.fit2c2)


#Anthropocentric Justification score
plor.fit3c2<- polr(comAntJtscore~  Condition +  SRFactsTotal +invitalscore  + inpsychscore + FirstLang, data = AC_df)

anova(plor.fit3c,plor.fit3c2)


#Biocentric choice score
plor.fit4c2 <- polr(comBioJFtotal ~  Condition +  SRFactsTotal +invitalscore  + inpsychscore + FirstLang, data = AC_df)

anova(plor.fit4c,plor.fit4c2)
```

# 7. For `Condition`, is there a significant difference in the dependent variables `MeanSeverity`, `BioJscore`, `AntJtscore`, and `BioJFtotal`?  
We did not find any evidence to conclude that `Condition` had an effect on any of the four dependent variables.  
  
## 7a. Visualization  
Looking at the distribution of Condition for each of the scores (for `MeanSeverity`, `BioJscore`, `AntJtscore`, and `BioJFtotal`) there is no clear visual pattern.  Though, these plots do not include any of the other predictor variables.

```{r echo=FALSE, warning=FALSE, message=FALSE}
#-----
#Calculate % in each of the MeanSeverity outcomes for Obj
Cond1_df <- AC_df %>% 
  filter(Condition=="Obj") %>% 
  group_by(comMeanSever, Condition) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

#Calculate % in each of the MeanSeverity outcomes for Nat
Cond2_df <- AC_df %>% 
  filter(Condition=="Nat") %>% 
  group_by(comMeanSever, Condition) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

#Calculate % in each of the MeanSeverity outcomes for Nat
Cond3_df <- AC_df %>% 
  filter(Condition=="Per") %>% 
  group_by(comMeanSever, Condition) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

Cond_df <- bind_rows(Cond1_df, Cond2_df, Cond3_df)

gg.1 <- ggplot(Cond_df, aes(x=comMeanSever, y=prop, fill=Condition)) +
  geom_col(color="white", position = position_dodge2(width = 0.001, preserve = "single")) +
  labs(x="score", y="proportion") +
  coord_cartesian(ylim=c(0, .75), xlim=c(1,3)) +
  theme_minimal(base_size=8) +
  labs(title="Mean Severity for each Condition") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))

#-----
#Calculate % in each of the comBioJtscore outcomes for Obj
Cond1_df <- AC_df %>% 
  filter(Condition=="Obj") %>% 
  group_by(comBioJtscore, Condition) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

#Calculate % in each of the comBioJtscore outcomes for Nat
Cond2_df <- AC_df %>% 
  filter(Condition=="Nat") %>% 
  group_by(comBioJtscore, Condition) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

#Calculate % in each of the comBioJtscore outcomes for Nat
Cond3_df <- AC_df %>% 
  filter(Condition=="Per") %>% 
  group_by(comBioJtscore, Condition) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

Cond_df <- bind_rows(Cond1_df, Cond2_df, Cond3_df)

gg.2 <- ggplot(Cond_df, aes(x=comBioJtscore, y=prop, fill=Condition)) +
  geom_col(color="white", position = position_dodge2(width = 0.001, preserve = "single")) +
  labs(x="score", y="proportion") +
  coord_cartesian(ylim=c(0, .75), xlim=c(1,3)) +
  theme_minimal(base_size=8) +
  theme(legend.position="none") +
  labs(title="Biocentric Justification for each Condition") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))
#-----

#Calculate % in each of the comAntJtscore outcomes for Obj
Cond1_df <- AC_df %>% 
  filter(Condition=="Obj") %>% 
  group_by(comAntJtscore, Condition) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

#Calculate % in each of the comAntJtscore outcomes for Nat
Cond2_df <- AC_df %>% 
  filter(Condition=="Nat") %>% 
  group_by(comAntJtscore, Condition) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

#Calculate % in each of the comAntJtscore outcomes for Nat
Cond3_df <- AC_df %>% 
  filter(Condition=="Per") %>% 
  group_by(comAntJtscore, Condition) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

Cond_df <- bind_rows(Cond1_df, Cond2_df, Cond3_df)

gg.3 <- ggplot(Cond_df, aes(x=comAntJtscore, y=prop, fill=Condition)) +
  geom_col(color="white", position = position_dodge2(width = 0.001, preserve = "single")) +
  labs(x="score", y="proportion") +
  coord_cartesian(ylim=c(0, .75), xlim=c(1,3)) +
  theme_minimal(base_size=8) +
  theme(legend.position="none") +
  labs(title="Anthropocentric Justification for each Condition") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))
#-----

#Calculate % in each of the comBioJFtotal outcomes for Obj
Cond1_df <- AC_df %>% 
  filter(Condition=="Obj") %>% 
  group_by(comBioJFtotal, Condition) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

#Calculate % in each of the comBioJFtotal outcomes for Nat
Cond2_df <- AC_df %>% 
  filter(Condition=="Nat") %>% 
  group_by(comBioJFtotal, Condition) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

#Calculate % in each of the comBioJFtotal outcomes for Nat
Cond3_df <- AC_df %>% 
  filter(Condition=="Per") %>% 
  group_by(comBioJFtotal, Condition) %>% 
  dplyr::summarise(n=n()) %>% 
  mutate(prop=n/sum(n))

Cond_df <- bind_rows(Cond1_df, Cond2_df, Cond3_df)

gg.4 <- ggplot(Cond_df, aes(x=comBioJFtotal, y=prop, fill=Condition)) +
  geom_col(color="white", position = position_dodge2(width = 0.001, preserve = "single")) +
  labs(x="score", y="proportion") +
  coord_cartesian(ylim=c(0, .75), xlim=c(1,3)) +
  theme_minimal(base_size=8) +
  theme(legend.position="none") +
  labs(title="Biocentric Choice for each Condition") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))
#-----

grid.arrange(gg.1, gg.2, gg.3, gg.4, ncol=2)
```
\newpage

## 7b. ANOVA test  
The ANOVA test for our models did not show any significant difference when we included/excluded the `Condition` variable.  The p-values for these differences are `MeanSeverity` ($p=0.62$), `BioJscore` ($p=0.75$), `AntJtscore` ($p=0.28$), and `BioJFtotal` ($p=0.68$).    
```{r echo=FALSE, comment=NA}
plor.fit1c3 <- polr(comMeanSever ~  SRFactsTotal + invitalscore  + inpsychscore + FirstLang + Age, data = AC_df)

anova(plor.fit1c, plor.fit1c3)


#Biocentric Justification score
plor.fit2c3 <- polr(comBioJtscore ~   SRFactsTotal +invitalscore  + inpsychscore + FirstLang + Age, data = AC_df)

anova(plor.fit2c, plor.fit2c3)


#Anthropocentric Justification score
plor.fit3c3<- polr(comAntJtscore~   SRFactsTotal +invitalscore  + inpsychscore + FirstLang + Age, data = AC_df)

anova(plor.fit3c,plor.fit3c3)


#Biocentric choice score
plor.fit4c3 <- polr(comBioJFtotal ~   SRFactsTotal +invitalscore  + inpsychscore + FirstLang + Age, data = AC_df)

anova(plor.fit4c,plor.fit4c3)

```
\newpage  

## 7c. Confidence intervals of the model coefficients  
We also looked at the 95% confidence intervals for the model coefficients.  For each dependent variable, the `Condition` coefficient's confidence interval included zero.  A coefficient of zero would mean that the predictor variable had no effect on the model.  So a confidence interval that includes zero, means that we can not conclude that the predictor variable has an effect on the dependent variable.

```{r echo=FALSE, message=FALSE, comment=NA}
#Meansever

plor.fit1c$call
confint(plor.fit1c)
#coefplot(plor.fit1c)
```


```{r echo=FALSE, message=FALSE, comment=NA}
#BioJtscore
plor.fit2c$call
confint(plor.fit2c)
#coefplot(plor.fit2c)
```

```{r echo=FALSE, message=FALSE, comment=NA}
#AntJtscore
plor.fit3c$call
confint(plor.fit3c)
#coefplot(plor.fit3c)
```

```{r echo=FALSE, message=FALSE, comment=NA}
#BioJFtotal
plor.fit4c$call
confint(plor.fit4c)
#coefplot(plor.fit4c)
```

